On the Construction of a Collision-Free Schedule of Beacons in a Wireless Multi-Hop Network

### 2013-10-07 paper.tex
explained MAC

The nodes share this information with their neighbours and then adjusts its own schedule according to the following rules.
\begin{iteration}
\item The schedule is doubled if any of the neighbours report occupation equal to 100\%.
\item The schedule is doubled halved if all the neighbors report occupation higher than 75\%.
\item The schedule is halved if all the neighbors report occupation lower than 25\%.
\end{iteration}

\section{The Medium Access Control Protocol}
\section{Conclusion}
\label{sec:conclusion}

>>>>

The nodes share this information with their neighbours and then adjusts its own schedule according to the following rules.
\begin{itemize}
\item The schedule is doubled if any of the neighbours report occupation equal to 100\%.
\item The schedule is doubled halved if all the neighbors report occupation higher than 75\%.
\item The schedule is halved if all the neighbors report occupation lower than 25\%.
\end{itemize}

\section{Data Included in the Beacons}
In each beacon, a node includes acknowledgements off all the beacons received in the last schedule, including their position.

For example, node A in Fig.~\ref{fig:topology} in its second transmission in Fig.~\ref{fig:timeline} includes the following information (assuming that it has received all the beacons correctly):
\begin{itemize}
\item Position 0: empty beacon
\item Position 1: beacon B
\item Position 2: beacon F
\item Position 3: beacon A
\end{itemize}

Each node also includes information of the data that it has stored in its queues for each of its neighbours.
\begin{itemize}
\item Position 0: empty beacon
\item Position 1: beacon B, 2 outstanding packets
\item Position 2: beacon F, 0 outstanding packets
\item Position 3: beacon A
\end{itemize}

A \emph{free flag}.
If a station has no data to transmit and no data to receive, it activates the free flag to indicate its neighbours that they can compete for the medium.

Acknowledgements of all the packets received since the previous beacon.

\section{The Medium Access Control Protocol}
Each station owns the time that follows its beacon until the next beacon spot.
It can use this time to transmit packets to its neighbours and to request packets from its neighbours using \emph{poll} packets.

A station can also indicate that it is not going to use the time that it owns using the free flag.

After empty beacon spots and after beacons with an activated free flag, stations are allowed to contend for the medium using CSMA/CA.
During this contention, they are exposed to hidden terminal collisions.

Note that packet transmission is not immediately followed by an acknowledgement as in traditional CSMA/CA.
Acknowledgements are delayed and transmitted together with beacons.

\section{Conclusion}
\label{sec:conclusion}
